\section*{\Huge Abstract}

Trajectory optimization offers mature tools for motion planning in high-dimensional spaces under dynamic constraints. However, in obstacle-cluttered environments, the non-convexity of the free space typically forces roboticists to rely on sampling-based planners, which struggle with high dimensions and differential constraints. Here, we demonstrate that convex optimization can reliably solve these problems through the convex decomposition of the free space.
Specifically, we decompose the collision-free configuration space into finite convex regions, organizing them into a Graph of Convex Sets (GCS). By combining Bézier curves with this graph structure, we formulate the motion planning problem as a compact mixed-integer convex program that naturally handles collision avoidance, velocity, and duration constraints.
We validate GCS across a spectrum of environments with increasing complexity, ranging from simple 2D obstacles and cluttered mazes to dynamical quadrotors and high-dimensional 7-DoF manipulators. Numerical experiments demonstrate that GCS consistently outperforms widely-used sampling-based planners (e.g., PRM). 
Specifically, in high-dimensional tasks, GCS reduces online query time by up to an order of magnitude compared to standard PRM, while finding globally optimal trajectories that are significantly shorter (up to 40\% reduction in length) than those from post-processed sampling-based planners \cite{motionplanning2022}. Ultimately, this work brings the reliability and speed of convex optimization to the traditionally challenging domain of nonconvex motion planning.
